Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-08-01 Rdocs/ManuscriptLPP.Rmd
adding materials and water quality tables

@@

```{r materials table}

@@

```{r pre-requisite scripts, eval =FALSE}
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/statistics.R") #script to analyze previously loaded data
source("Rscripts/plot_source.R") #source code for custom plotting functions

@@

```{r wq plots}
#water quality dot plots
#water quality by date on the y and site as color
wq_ts_BySite("P")
wq_ts_BySite("pH")
wq_ts_BySite("NH3")
wq_ts_BySite("DO")
wq_ts_BySite("Temp")
wq_ts_BySite("Cond")
wq_ts_BySite("Nitrogen")
wq_ts_BySite("Flow") + labs(title = "Flow rate seasonality",
                            x = "Date", y = "Flow (m/s)")
```

>>>>

```{r pre-requisite scripts, echo=FALSE}
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/statistics.R") #script to analyze previously loaded data
source("Rscripts/plot_source.R") #source code for custom plotting functions

@@

```{r materials table}
readxl::read_xlsx("Rfigs/summaryFigures.xlsx", sheet = 1) %>%
knitr::kable(caption = "Table 1: Cost and Mesh Size By Material")
```

@@

@@

```{r wq table}
readxl::read_xlsx("Rfigs/summaryFigures.xlsx", sheet = 2) %>%
knitr::kable(caption = "Table 2: Water quality parameters averaged over the course of the sampling period")
```

```{r wq plots, eval=FALSE}
#water quality dot plots
#water quality by date on the y and site as color
wq_ts_BySite("P")
wq_ts_BySite("pH")
wq_ts_BySite("NH3")
wq_ts_BySite("DO")
wq_ts_BySite("Temp")
wq_ts_BySite("Cond")
wq_ts_BySite("Nitrogen")
wq_ts_BySite("Flow") + labs(title = "Flow rate seasonality",
                            x = "Date", y = "Flow (m/s)")
```
